|

### 2020-05-18 paper/Manuscript.Rmd
marijn changes

One important impediment to comprehensive citation is the fact that print journals operate with space constraints.
Print journals often discourage comprehensive citation, either actively, or passively by including the reference list in the manuscript word count.
Researchers can overcome this impediment by preparing two versions of the manuscript:
One version with comprehensive citations for online dissemination, and another version for print, with only the essential citations.
The print version should reference the online version, so interested readers can find the comprehensive reference list.
Step 20 of the WORCS procedure suggests uploading the online version to a preprint server.
This is important because most preprint servers - [at least the ones listed by OSF.io](https://help.osf.io/hc/en-us/articles/360019930493-Preprint-FAQs#how_do_i_find_preprints) - are indexed by Google Scholar.
This means that authors will receive credit for cited work; even if they are cited only in the online version.
Moreover, preprint servers ensure that the online version will have a persistent DOI, and will remain reliably accessible, just like the print version.

>>>>

One important impediment to comprehensive citation is the fact that print journals operate with space constraints.
Print journals often discourage comprehensive citation, either actively, or passively by including the reference list in the manuscript word count.
Researchers can overcome this impediment by preparing two versions of the manuscript:
One version with comprehensive citations for online dissemination, and another version for print, with only the essential citations.
The print version should reference the online version, so interested readers can find the comprehensive reference list.
Step 20 of the WORCS procedure suggests uploading the online version to a preprint server.
This is important because most preprint servers - at least those hosted by the [Open Science Framework (OSF)](https://help.osf.io/hc/en-us/articles/360019930493-Preprint-FAQs#how_do_i_find_preprints) - are indexed by Google Scholar.
This means that authors will receive credit for cited work; even if they are cited only in the online version.
Moreover, preprint servers ensure that the online version will have a persistent DOI, and will remain reliably accessible, just like the print version.
